Reducing iptables configuration complexity using chains

### 2014-05-07 iptables/presentation.tex
use match, not filter, to better reflect iptables documentation
add slide on IPv6

    \frametitle{Filters}

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
\end{document}

>>>>

    \frametitle{Match}

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
  \begin{frame}
    \frametitle{IPv6}
    Configuration is the same for IPv4, use ip6tables :
    \begin{example}
      \small{ip6tables -P INPUT DROP\\
      ip6tables -P OUTPUT ACCEPT\\
      ip6tables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      ip6tables -A INPUT -p icmp -j ACCEPT \# allow ping, etc\\
      ip6tables -A INPUT -m state \dd state ESTABLISHED,RELATED -j ACCEPT}
    \end{example}
    Even if IPv4 rules are set, IPv6 has to be configured seperately, otherwise the defaults apply.
  \end{frame}
\end{document}
